\textbf{ \Large {Reducing data traffic in wireless structural health monitoring systems using embedded computing}}

### 2015-02-10 Paper/PaperJahrSchlichSHM.tex

%% The following parameters seem to provide a reasonable page setup.
%\topmargin -1.0cm
%\oddsidemargin 0.2cm
%\textwidth 15cm 
%\textheight 23cm
%\footskip 1.0cm

@@

%\todo{Bild ersetzen durch ein Bild mit den fertig installierten SPOTS}

@@

After the

@@

>>>>

@@

@@

@@

In a next step multiple sensor nodes are installed to different positions on the test structure in order to test the SHM system as a whole.
After the sensors are installed, the test structure was subjected to varying degrees of excitation.
The calculated natural frequencies, and corresponding magnitude, are safed in the MySQL database and analyzed manually.
The results of these test runs are shown in \autoref{tab:lab-ex} in the appendix.

Every sensor calculated the same natural frequency to a precision of four decimal points regardless of sensor position and degree of excitation.
The sensors installed on the top of the structure always calculates the highest corresponding magnitude and magnitudes decreased from top to bottom.
These results are plausible and indicate, that the SHM system is working correctly.

Through FFT analysis of oscillations the data traffic is decreased from 512 measured acceleration values per oscillation to two values, the natural frequency and the corresponding magnitude.
A number stored in the used data format double occupies 8\,bytes of space.
Therefore the data traffic was decreased by $510\times8\,B = 4080\,B = 3,98\,MB$ per sampling event
This equates a 99.6\,\% decrease of data traffic.
